Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
personal narrative to passive, also found a can not

The crucial point is to understand what happens when we can not derive $\theta$ deductively but must substitute it inductively with an estimate $\hat\theta(y)$.
Any estimated parameters $\hat{\theta}(y)$ would almost surely not be equal to $\theta_*$ (assuming $\theta$ may take an infinite number of values, i.e., is continues).
It follows, almost surely, that we lose information:
\begin{equation}
\mathcal{L}_{KL}(f, g(\cdot|\hat{\theta}(y)) > \mathcal{L}_{KL}(f, g(\cdot|\theta_*))
\end{equation}
Or ignoring the constant:
\begin{equation}
\mathbb{E}_{X \sim f}\left[\log(g(x|\theta_*))\right] >\mathbb{E}_{X \sim f}[\log(g(x|\hat{\theta}(y)))] 
\end{equation}

>>>>

The crucial point is to understand what happens when $\theta$ cannot be derive deductively but must be substituted inductively with an estimate $\hat\theta(y)$.
Any estimated parameters $\hat{\theta}(y)$ would almost surely not be equal to $\theta_*$ (assuming $\theta$ may take an infinite number of values, i.e., is continues).
It follows, almost surely, that we lose information:
\begin{equation}
\mathcal{L}_{KL}(f, g(\cdot|\hat{\theta}(y)) > \mathcal{L}_{KL}(f, g(\cdot|\theta_*))
\end{equation}
Or ignoring the constant:
\begin{equation}
\mathbb{E}_{X \sim f}\left[\log(g(x|\theta_*))\right] >\mathbb{E}_{X \sim f}[\log(g(x|\hat{\theta}(y)))] 
\end{equation}
